Individual_Pop_Analysis

### 2021-09-24 IndividualPops/CMPSubpop.Rmd
streamlining individualPops analyses

## DGE w/ resolution = 0.5
Strt with comparing all clusters against all other clusters and write out cluster info
calculate `FindAllMarkers()` for different idents and save to new file
```{r}
# ident.list <- colnames(seurat.object@meta.data)[grepl("^RNA_snn", colnames(seurat.object@meta.data))]
ident.list <- c("RNA_snn_res.0.5", "RNA_snn_res.1")

>>>>

## DGE
Strt with comparing all clusters against all other clusters and write out cluster info
calculate `FindAllMarkers()` for different idents and save to new file
```{r}
# ident.list <- colnames(seurat.object@meta.data)[grepl("^RNA_snn", colnames(seurat.object@meta.data))]
ident.list <- c("RNA_snn_res.0.5", "RNA_snn_res.1")

### 2021-09-24 IndividualPops/Individual_SubpopAnalyses.Rmd
streamlining individualPops analyses

## Set global variables
```{r}
pop.id <- "GMP"
folder.appendix <- "m"
fav.var <- 80
object.res <- ".1"
ident.list <- c("RNA_snn_res.0.5", "RNA_snn_res.1")
```

@@

```{r}
xprsn.mtx <- t(as.data.frame(as.matrix(seurat.object@assays$RNA@counts))[rownames(as.data.frame(as.matrix(seurat.object@assays$RNA@counts))) %in% probe.list, ])
head(xprsn.mtx[1:5, 1:5])
```
```{r}
biomark.export <- merge(xprsn.mtx, seurat.object@meta.data["RNA_snn_res.1"], by = 0)
```
```{r}
write.table(biomark.export, file = paste0(projectName, "_Counts-BiomarkProbes.txt"), sep = "\t", quote = FALSE, col.names = TRUE, row.names = FALSE)
```

>>>>

## Set global variables
```{r}
pop.id <- "CMP"
folder.appendix <- "m2"
fav.var <- 80
object.res <- ".1"
ident.list <- c("RNA_snn_res.0.5", "RNA_snn_res.1")
```

@@

```{r}
xprsn.mtx <- t(as.data.frame(as.matrix(seurat.object@assays$RNA@counts))[rownames(as.data.frame(as.matrix(seurat.object@assays$RNA@counts))) %in% probe.list, ])
biomark.export <- merge(xprsn.mtx, seurat.object@meta.data["RNA_snn_res.1"], by = 0)
write.table(biomark.export, file = paste0(projectName, "_Counts-BiomarkProbes.txt"), sep = "\t", quote = FALSE, col.names = TRUE, row.names = FALSE)

xprsn.mtx <- t(as.data.frame(as.matrix(seurat.object@assays$RNA@data))[rownames(as.data.frame(as.matrix(seurat.object@assays$RNA@data))) %in% probe.list, ])
biomark.export <- merge(xprsn.mtx, seurat.object@meta.data["RNA_snn_res.1"], by = 0)
write.table(biomark.export, file = paste0(projectName, "_Data-BiomarkProbes.txt"), sep = "\t", quote = FALSE, col.names = TRUE, row.names = FALSE)

xprsn.mtx <- t(as.data.frame(as.matrix(seurat.object@assays$RNA@scale.data))[rownames(as.data.frame(as.matrix(seurat.object@assays$RNA@scale.data))) %in% probe.list, ])
biomark.export <- merge(xprsn.mtx, seurat.object@meta.data["RNA_snn_res.1"], by = 0)
write.table(biomark.export, file = paste0(projectName, "_ScaleData-BiomarkProbes.txt"), sep = "\t", quote = FALSE, col.names = TRUE, row.names = FALSE)
